Draft

### 2017-08-12 Thesis/Draft.tex
Add exponential family to draft

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

In a standard parametric testing problem, we have drawn an iid sample
\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
random variable \(X_i\). We assume that \(X_i\) follows some
distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). In a
standard hypothesis test, we would then want to test whether an
alternative parameterization is more likely than the parameterization
given by the null hypothesis. That is, we test

@@

In order to assess whether the \(H_0\) hypothesis can be rejected, one
computes the likelihood \(L(x|\theta)\) of the observed sample under
both parameterizations: \(L_{H_0} = L(x|\theta = \theta_{H_0})\) and
\(L_{H_1} = L(x|\theta = \theta_{H_1})\). The likelihood ratio test
statistic is then given as

\[
LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}}.
\] The intuition behind the test of course being that, if the true
parameterization is \(H_1\) and not \(H_0\), then the likelihood
\(L_{H_1}\) should be larger than \(L_{H_0}\). A small enough likelihood
ratio would thus lead us to a rejection of the null hypothesis, while a
large likelihood ratio is evidence in favor of the null hypothesis.

@@

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
\hypersetup{unicode=true,
            pdftitle={Draft},
            pdfauthor={Tim Radtke},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

In a standard parametric testing problem, we have drawn an iid sample
\(x = (x_1, ..., x_T)\), where each \(x_i\) is a realization from the
random variable \(X_i\). We assume that \(X_i\) follows some probability
distribution \(Q(\theta)\) paramaterized by a vector \(\theta\). Let
\(q(x;\theta)\) be the density function corresponding to the
distribution. In a standard hypothesis test, we test whether an
alternative parameterization is more likely than the parameterization
given by the null hypothesis. That is, we test

@@

In order to assess whether the \(H_0\) hypothesis can be rejected, one
computes the likelihood \(L(x|\theta)\) of the observed sample under
both parameterizations:
\(L_{H_0} = L(x|\theta = \theta_{H_0}) = \prod_{i=1}^T q(x_i|\theta_{H_0})\)
and
\(L_{H_1} = L(x|\theta = \theta_{H_1}) = \prod_{i=1}^T q(x_i|\theta_{H_1})\).
The likelihood ratio test statistic is then given as

\[
LR(\theta_{H_0}|| \theta_{H_1}) = \frac{L_{H_0}}{L_{H_1}} = \prod_{i=1}^T\frac{q(x_i|\theta_{H_0})}{ q(x_i|\theta_{H_1})}.
\] The intuition behind the test of course being that, if the true
parameterization is \(H_1\) and not \(H_0\), then the likelihood
\(L_{H_1}\) should be larger than \(L_{H_0}\). A small enough likelihood
ratio would thus lead us to a rejection of the null hypothesis, while a
large likelihood ratio is evidence in favor of the null hypothesis.

By considering \(lr = -2\log(LR(\theta_{H_0}|| \theta_{H_1}))\), one has
a statistic that is \(\chi^2\) distributed with degrees of freedom that
depend on the null and alternative hypothesis. Assessing whether the
null hypothesis can be rejected with large confidence thus becomes
straightforward.

@@

The simple concept of the likelihood-ratio test serves as foundation for
a new sampling strategy that can be applied to the thresholding bandit
problem. In contrast to the cumulative regret problem, or even the best
arm identification problem, we have some sort of null hypothesis for the
distributions in the thresholding bandit problem. In case of no
information and no observed samples, the null hypothesis might simply be
that all distributions have a mean that equals the threshold. By
observing samples, we then want to test whether the mean of the
distributions is different from the threshold \(\tau\) in either
direction. Once we are sure that there is a difference, we do not want
to continue to test. Instead, we would like to focus our sampling effort
on a different arm where we are not as sure. The likelihood ratio
quantifies how ``significant''" of a difference there is between the
threshold \(\tau\) and the current sample mean \(\hat{\mu}_i(t)\) of an
arm. Given that we plug in the sample mean, that is, the maximum
likelihood estimator for the true mean for many distributions, the
likelihood ratio will be smaller than 1 and decrease in sample size even
if the threshold and sample mean are constant.

Due to these characteristics, the likelihood ratio can serve as a
natural index for sampling strategies. Thus write as index

\[
B_i(t) = LR(\tau|| \hat{\mu}_i(t)) = \prod_{i=1}^T\frac{q(x_i|\tau)}{ q(x_i|\hat{\mu}_i(t))}
\]

and pull at round \(t\) the arm \(i^* = \arg \max_i B_i(t)\). As we
described in the previous paragraph, we have \(B_i(t) \leq 1\),
\(t \uparrow \rightarrow B_i(t) \downarrow\), and
\(|\hat{\mu}_i(t) - \tau| \uparrow \rightarrow B_i(t) \downarrow\).
Consequently, by choosing the arm that maximizes \(B_i(t)\), we choose
an arm for which we either have not collected many samples, or where the
sample mean is close to the threshold \(\tau\). In this sense, a
strategy based on the likelihood ratio is of course very reminiscient of
the index employed by the APT algorithm. Indeed, assuming the samples
are normally distributed with the same variance for the distribution
\(\nu_i\) under both \(H_0\) and \(H_1\), then
\(-\log(LR(\tau||\hat{\mu}_i(t)))\) equals the index in APT. Why then
would one use the likelihood based strategy?

Given that the APT index and the likelihood-ratio based index are only
equivalent for normally distributed random variables with fixed standard
deviation, the new strategy promises efficiency improvements whenever
the true distribution is known and different from the normal
distribution. The most important example are Bernoulli arms with small
means as discussed before. Here, it is also easy to assume that the true
distribution is known upfront. Similarly, the likelihood ratio statistic
can be used for other univariate distributions of the exponential
family. But we also propose a version for the Normal distribution with
unknown mean.

We now focus on the case where the distributions
\(\nu_{\theta_1}, ..., \nu_{\theta_K}\) are all the same canonical
exponential family of distributions with scalar parameter
\(\theta_i \in \Theta\). The probability density function of the
absolutely continuous distribution \(\nu_{\theta_i}\) with regard to a
dominating measure \(\rho\) on \(\mathbb{R}\) is given by
\(q(x|\theta) = h(x) \exp(T(x)\theta - b(\theta))\). As described in
Cappé et al. (2013), citing Lehmann and Casella (1998), the derivative
\(b'(\theta)\) of \(b(\theta)\) is an increasing continuous function
such that the expected value \(\mathbb{E}(\nu_{\theta}) = b'(\theta)\)
for all \(\theta \in \Theta\). Given that \(b'(x)\) is strictly convex,
we have a one-to-one relation between \(b'(\theta)\) and
\(\mathbb{E}(\nu_{\theta})\) through the continuous inverse
\(b'^{-1}(\theta)\). Consequently, one can just as well parameterize the
distribution its mean \(\mu = \mathbb{\nu_{\theta}}\) and write
\(\nu_{b'^{-1}(\mu)}\) with the probability density function

\[
q(x|b'^{-1}(\mu)) = h(x) \exp(T(x) b'^{-1}(\mu) - b(b'^{-1}(\mu))).
\]

This lets us write the likelihood ratio for the exponential family
distributions as

\[
LR(b'^{-1}(\mu_0)||b'^{-1}(\mu_1)) = \prod_{i=1}^n \frac{\exp(T(x_i) b'^{-1}(\mu_0) - b(b'^{-1}(\mu_0)))}{\exp(T(x_i) b'^{-1}(\mu_1) - b(b'^{-1}(\mu_1)))}
\]

or if we write it as negative log-likelihood ratio:

\[
-\log(LR) = n\Big(b\big(b'^{-1}(\mu_0)) - b(b'^{-1}(\mu_1)\big)\Big) - \Big(b'^{-1}(\mu_0)-b'^{-1}(\mu_1)\Big)\sum_{i=1}^nT(x_i)
\]

As we will see now, this statistic is easily derived for many specific
distributions.

\paragraph{Example 1: Bernoulli
Distribution}\label{example-1-bernoulli-distribution}

We have \(T(x_i) = x_i\), \(\theta = \log(\mu/(1-\mu))\),
\(\Theta = (0,1)\), \(b(\theta) = \log(1+\exp(\theta))\), and
\(\mu \in (0,1)\). Then \(b'(\theta) = \mu\), and we can write

\[
-\log(LR(\mu_0||\mu_1)) = n(\log\Big(\frac{1-\mu_0}{1-\mu_1}\Big)) - \Big(\log(\frac{\mu_0}{1-\mu_0}) - \log(\frac{\mu_1}{1-\mu_1})\Big)\sum_{i=1}^{n}x_i = (1-\hat{\mu})\log\Big(\frac{1-\mu_1}{1-\mu_0}\Big) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0})
\]

We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
then

\[
-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau)
\]

\paragraph{Example 2: Poisson
Distribution}\label{example-2-poisson-distribution}

We have \(T(x_i) = x_i\), \(\theta = \log(\mu)\),
\(\Theta = \mathbb{R}\), \(b(\theta) = \exp(\theta)\), and
\(\mu \in (0, +\infty)\). Then \(b'(\theta) = \mu\), and we can write:

\[
-\log(LR(\mu_0||\mu_1)) = n(\mu_0 - \mu_1) - (\log(\mu_0) - \log(\mu_1))\sum_{i=1}^n x_i = (\mu_0 - \mu_1) + \hat{\mu}\log\Big(\frac{\mu_1}{\mu_0}\Big)
\]

We observe that, if we let \(\mu_0 = \tau\) and \(\mu_1 = \hat{\mu}\),
then

\[
-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = (\tau - \hat{\mu}) + \hat{\mu}\log\Big(\frac{\hat{\mu}}{\tau}\Big)
\]

\paragraph{\texorpdfstring{Example 3: Normal distributions with known
variance
\(\sigma^2\)}{Example 3: Normal distributions with known variance \textbackslash{}sigma\^{}2}}\label{example-3-normal-distributions-with-known-variance-sigma2}

We have \(T(x_i) = x_i\), \(\theta = \mu/\sigma^2\),
\(\Theta = \mathbb{R}\), \(b(\theta) = \sigma^2\theta^2/2\),
\(\mu \in \mathbb{R}\). Then \(b'(\theta) = \mu\), and we can write

\[
-\log(LR(\mu_0||\mu_1)) = n (\frac{\mu_0^2}{2\sigma^2} - \frac{\mu_1^2}{2\sigma^2}) - (\frac{\mu_0}{\sigma^2} - \frac{\mu_1}{\sigma^2})\sum_{i=1}^nx_i = \frac{1}{2\sigma^2}\Big(\mu_0^2-\mu_1^2 - 2\mu_0\hat{\mu} + 2\mu_1\hat{\mu}\Big)
\]

And again, if we let \(\mu_1 = \hat{\mu}\) and \(\mu_0 = \tau\), then

\[
-\log(LR(\tau||\hat{\mu})) = KL(\nu_{b'^{-1}(\hat{\mu})}||\nu_{b'^{-1}(\tau)}) = d(\hat{\mu},\tau) = \frac{(\hat{\mu} - \tau)^2}{2\sigma^2}.
\]

\section{Experiments}\label{experiments}

\subsection{Real Data}\label{real-data}

We show two experiments that were performed on real data. While most
papers in the multi-armed bandit literature resort to synthetic data to
assess the performance of algorithms -- just as we have done in the
previous chapter -- we have tried to acquire real world data. This data
is what bandit algorithms are used for in practice, and does not fulfill
the standard independence and identical distribution assumptions as
nicely. The real data thus can be considered a first robustness test for
the algorithms.

\subsubsection{The Data Set}\label{the-data-set}

The data have been collected by the German ecommerce company
\href{https://amorelie.de}{Amorelie} as part of standard website
performance tracking. For 197 selected products, we have the number of
users visiting each product's detail page (PDP) at a given minute. The
data set we use here has been collected during the entire month of
November 2016. It can be considered time series data collected at
minutely frequency. Thus the data contain 43200 observations per
product, and overall 8510400 observations.

Given that we want to run an offline comparison of bandit algorithms, it
is important to have at each time point an observation for each arm.
Given that, it is easy to evaluate the perfomance of algorithms that
make different decisions at different point in times and thus do not
observe the same samples. By having an observation for each arm at any
given time point, each algorithm had at least the opportunity to observe
a certain sample. Other papers (CITE YAHOO!) have solved this problem by
using a sample drawn uniformly during for example an A/B test. Then, if
the next observation in the sample is not from the same arm that the
algorithm would like to draw from, observations are discarded until the
next observation from the selected arm.

The choice of having basically multiple time series data as the sample
leads to a simple way of running the algorithms just as often on the
data as for simulated data. In particular, the goal is to perform 5000
runs over the sample to confidently assess the performance. Since we
wanted to preserve the potential time dependency of the data, a simple
resampling of the data was not an option to create the needed 5000
variations of the sample. Thus what we did instead was a form of time
series cross validation. To preserve the autocorrelation, one can create
different samples of \(X\) observations by sliding a window of size
\(X\) over the time series. Moving the window one period (in our case
minute) at a time, one ensures that no sample shares start and end
observation with another sample. In particular, this means for a given
bandit strategy and two samples that the observations that the algorithm
collects as feedback during the two initialization phases differ from
sample to sample and are never the same. This is because during
initialization every strategy pulls arms \(1, ..., K\) once in this
order.

While the data is count data (the number of visits to a PDP during a
given minute), we binarize the data by applying a certain threshold. If
the counts is above this threshold, the observation becomes a \(1\),
else \(0\). Thus we have a binary time series of length 43200 for each
of the 197 products. Given that the number of visitors that come to a
given PDP is likely to vary by time of day and by day, and in general
over time, we expect that the mean of the time series to not be stable
over time. For example, less visitors will come during night than during
evening, thus leading to a decreasein the average. On the other hand,
more users may visit the site during a weekend, thus leading to a spike
on Saturdays and Sundays. Because of the latter time dependency, it is
best practice to run online A/B tests for at least a week, or an integer
multiple of weeks, so as to take into account the weekly seasonality in
the time series. For this reason, the experiments we present below were
run on \(60 \cdot 24 \cdot 7 = 10080\) observations for each arm, so as
to have a sample for one full week.

We can look at summary statistics for the sample means of the 197
products over the month of November to get a first idea of the data we
are dealing with. We see that most products have a low mean, which is
very common also for actual conversion rate data that would be tested
with A/B tests or multi-armed bandits. Yet the sample of products
contains a few outliers with very large view rates, with a maximum rate
of 78\%. If we used a threshold \(\gamma\) to binarize the count data,
then this means that on average every fourth minute the count of
visitors was below \(\gamma\) for this product. On the other hand, we
conclude that using thresholding bandit strategies to test the products
against a threshold of for example \(\tau = \frac{2}{60} = 0.333\) or
\(\tau = \frac{5}{60} = 0.083\) is likely to create more complex
problems than a threshold of, say, \(\tau = \frac{15}{60} = 0.25\)
would.

\begin{longtable}[]{@{}rrrrrr@{}}
\caption{Summary Statistics for View Rates of 197
Products}\tabularnewline
\toprule
Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
Maximum\tabularnewline
\midrule
\endfirsthead
\toprule
Mean & Minimum & 25\% Quantile & Median & 75\% Quantile &
Maximum\tabularnewline
\midrule
\endhead
0.12 & 0 & 0.036 & 0.074 & 0.136 & 0.778\tabularnewline
\bottomrule
\end{longtable}

\subsubsection{\texorpdfstring{Experiment 1:
\(\tau = \frac{2}{60}\)}{Experiment 1: \textbackslash{}tau = \textbackslash{}frac\{2\}\{60\}}}\label{experiment-1-tau-frac260}

In this first experiment, we pick ten arms randomly from the set of 197
arms. The experiment is run on these 10 arms with a budget of
\(T=10080\) samples during each of the \(5000\) iterations for which we
repeat the experiment. Given the time series cross-validation idea
described above, this means that in total, \(15080\) observations of the
available \(43200\) available observations per arm are used in training.
In the thresholding bandit problem, we classify arms as below or above a
threshold. Thus we can evaluate the strategies also based on whether
their classifications are correct in a holdout sample. As this holdout
sample, we can use the 10080 observations in our data set that follow
the first 15080 observations used in training. In the table below, we
present the count rates of the ten products for both training and test
samples.

\begin{longtable}[]{@{}lrrrrrrrrrr@{}}
\caption{Count rates for ten products for both training and test
sample.}\tabularnewline
\toprule
& V64 & V1 & V159 & V119 & V70 & V114 & V189 & V139 & V118 &
V148\tabularnewline
\midrule
\endfirsthead
\toprule
& V64 & V1 & V159 & V119 & V70 & V114 & V189 & V139 & V118 &
V148\tabularnewline
\midrule
\endhead
Training & 0.027 & 0.001 & 0.013 & 0.158 & 0.071 & 0.071 & 0.059 & 0.053
& 0.156 & 0.102\tabularnewline
Test & 0.022 & 0.000 & 0.011 & 0.130 & 0.064 & 0.060 & 0.058 & 0.055 &
0.150 & 0.115\tabularnewline
TrainingMinusTau & -0.006 & -0.033 & -0.021 & 0.125 & 0.038 & 0.038 &
0.026 & 0.019 & 0.123 & 0.068\tabularnewline
\bottomrule
\end{longtable}

We see that while the rates do vary across samples, they are relatively
stable which is likely due to the fact that the samples come from an
entire week's worth of observations. In particular, since we test
against a threshold of \(\tau = \frac{2}{60} = 0.333\) in this
experiment, the classifications of arms do not differ across training
and test data. A correct classification after training will be correct
in the test set. For the rest of the analysis, we thus evaluate the
performance using the training rates.

When comparing the rates against the threshold, we see that three
products are below the already small threshold. Product \(V64\) seems to
be especially difficult to classify correctly, even without time
dependency. On the other hand, arms \(V119\) and \(V118\) should be much
easier than the rest.

In order to visualize the time dependency that we expect for our
samples, we plot a moving average of the mean of the time series for the
first week of data. To remove the daily seasonality, we select a moving
average window of \(60\cdot24 = 1440\) observations. To make the time
dependency even more obvious, we contrast the actual data against
synthetic data generated using the sample means of the actual data.

The graph again underlines that arm \(V64\) is likely to be very
difficult to classify given that it's moving average even crosses the
threshold twice. The same is true for arm \(V139\), which is not visible
when considering the overall mean alone. Furthermore, arms \(V159\) and
\(V189\) come very close to the threshold at times.

\includegraphics{Draft_files/figure-latex/unnamed-chunk-4-1.pdf}

\subsubsection{\texorpdfstring{Experiment 2:
\(\tau = \frac{5}{60}\)}{Experiment 2: \textbackslash{}tau = \textbackslash{}frac\{5\}\{60\}}}\label{experiment-2-tau-frac560}
